---
title: "Solution to hands-on exercices"
author: "Gilles Kratzer"
date: "10/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Warm up question: Why doing a sample size prior to your study?

1. A sample size calculation estimates not only how many participants/subjects/animals you need, but how many you do not need. 
2. Sometime required by granting agency or ethic committee.
3. The biggest benefit of doing these calculations is to not waste years and thousands of dollars in grants or tuition pursuing an impossible analysis. 

### 1. Estimate the require sample size for a parametric approach

```{r}
power.t.test(delta = 30,sd = 30,sig.level = .05,power = .8,type = "two.sample",alternative = "two.sided")
```
### 2. Estimate the new required sample size if SD is reduced by 20%

```{r}
power.t.test(delta = 30,sd = 24,sig.level = .05,power = .8,type = "two.sample",alternative = "two.sided")
```
### 3. Estimate the new sample size is the SD is 30 [ms] but the expected change is an increase of 36 [ms]
```{r}
power.t.test(delta = 36,sd = 30,sig.level = .05,power = .8,type = "two.sample",alternative = "two.sided")
```
### 4. Estimate the new sample size if you decide to use a paire designed
```{r}
power.t.test(delta = 30,sd = 30,sig.level = .05,power = .8,type = "paired",alternative = "two.sided")
```
### 5. Estimate the power achieved with 10 subject per group in an unpair design

```{r}
power.t.test(n = 12,delta = 30,sd = 30,sig.level = .05,type = "two.sample",alternative = "two.sided")
```